IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/conclusion.tex
yo

We presented a formal semantics which describes how to extend arbitrary languages
with language-based coarse-grained IFC. We prove the security guarantees
TSNI and TINI, where the proof technique is parametrized on the
target language, for two scheduling policies. In
addition, we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice. Finally, we described extensions to
the core IFC language with more advanced concepts like labeled values, privileges,
and a notation of clearance, and therefore connecting it with existing
IFC implementations for Javascript, Haskell, and (in
less detail) proposing IFC for C.

>>>>

We presented a formal semantics which describes how to extend arbitrary languages
with language-based coarse-grained IFC. We prove the security guarantees
TSNI and TINI, where the proof technique is parametrized on the
target language, for two scheduling policies. In
addition, we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice. Finally, we described extensions to
the core IFC language with more advanced concepts like labeled values, privileges,
and a notion of clearance, and therefore connecting it with existing
IFC implementations for JavaScript, Haskell, and (in
less detail) proposing IFC for C. With this work, we aim to expose how ideas
from IFC in OS can be systematically applied in programming languages.
